---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  error = TRUE
)
library(binomial)
```

# Binomial Variable Package

## Creating a binomial random variable
```{r}
X <- bin_variable(trials=10,prob=0.3)
```

#### Print and Display the Summary Statistics
```{r}
print(X)
summary(X)
```

A summary function call outputs the following statistics of the created binomial variable:

+ mean
+ variance
+ mode
+ skewness
+ kurtosis

Access a specific statistic separately like so:
```{r}
summary(X)$mean
summary(X)$skewness
```

## Additional functions unrelated to binomial object
### Auxiliary functions to calculate above statistics without explicit creation of a binomial variable
```{r}
bin_mean(trials=10, prob=0.3)
bin_variance(trials=10, prob=0.3)
bin_mode(trials=10, prob=0.3)
bin_skewness(trials=10, prob=0.3)
bin_kurtosis(trials=10, prob=0.3)
```

#### Calculate the number of possible combinations choosing k items from n total
```{r}
bin_choose(n=10, k=3)
```

#### Calculate the probability of getting a certain number of successes, given a number of trials and probability of success on each trial
```{r}
bin_probability(success=2, trials=5, prob=0.5)
```

#### Return a distribution with the number of possible successes and probability of each outcome
```{r}
bin_distribution(trials=5, prob=0.3)
```

#### Return a distribution with the number of possible successes, probability of each outcome, and the cumulative probability of getting at most each number of success
```{r}
bin_cumulative(trials=5, prob=0.3)
```

#### Both distribution can be visualized in a histogram
```{r}
plot(dist)
plot(cumu)
```
